Gravitational Lens Recovery with \Glass: How to measure the mass profile and shape of a lens

### 2014-01-21 limits/ms.tex
Plots.
Updated plots.
New plot of sigp without stellar mass.
Commented out Figure 9. Split shape plots into two.

@@

\begin{table}
\begin{tabular}{llllllll}
Galaxy & $\gamma_\star$ & $M_\star$ & $\gamma_\mathrm{DM}$ & $M_\mathrm{DM}$ & $\Rmap$ \\
\hline
DM-ctr,DM-core & 1 & 4 & 0.05 & $11^{2.95}$ & 50 kpc\\ % AA
DM-ctr,DM-cusp & 1 & 4 & 1 & $11^2$ & 50 kpc \\ % AC
S-ctr,DMcore & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ & 50 kpc \\ % BB
S-ctr,DMcusp & 1.5 & $2^{1.5}$ & 1 & $11^2$ & 10 kpc %BC
\end{tabular}
\caption{Profile parameters for the four mock galaxies. The name indicates whether 
  the galaxy is centrally dark matter or stellar dominated with a shallow or cuspy 
  dark matter density profile.  Masses are in units of
  $1.8\e{10}\Msun$. The scale lengths for all lenses are
  $(a_\star,a_\mathrm{DM})=(2,20)$\,kpc. $\Rmap$ is the 2D projected radius
used to generate the lens configurations.}
\label{mock galaxy params}
\end{table}

@@

\begin{figure*}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-a.pdf}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-b.pdf}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-c.pdf}
\caption{
  \sout{{\bf JR. Need to homogenise plot dimensions here. Larger fonts as in Figure 1 are also required.} }
A typical reconstructed lens. Here we present results for a single quad image lensed by the Sdom/DMcuspy mock galaxy.
\textbf{Left:}
The arrival time surface. 
\textbf{Middle:}
The surface density. The magenta curve represents the dark matter component,
the yellow curve the stellar component, and the blue curve is the sum of the two.
The black curve comes from the original mass model used to create the lens.
The green vertical lines mark the radial positions of the images. The higher
resolution feature of \Glass\ has been used on the central pixel allowing the
steep profile to be captured.
\textbf{Right:}
The cumulative mass. The error bars on both plots are $1\sigma$.}
\label{reconstruction}
\end{figure*}

@@

\begin{figure*}
\plotthree{AAExtendedDoubleR1_TmS-shape-hist-11.pdf} {AAferror_shape-1sig.pdf} {BBferror_shape-1sig.pdf}\\
\plotthree{BCZContrastR1R3_TmS-shape-hist-212.pdf} {ACferror_shape-1sig.pdf} {BCferror_shape-1sig.pdf}
\caption{ The two plots in the left most column show sample distributions of
  $s=\lambda_1/\lambda_2$, the ratio of the largest to smallest principal axes.
  The upper (poor) plot is from the DMdom/DMshallow galaxy, while the lower (good) plot is
  from the Sdom/DMcuspy galaxy. The black vertical lines mark the $1\sigma$
  region and the vertical blue line is the value of $s$ for the corresponding
  mock galaxy. The remain four plots are similar to those in \figref{main
  results pixel-wise} and show the fractional error of $s$ over all the models,
with respect to the mock galaxies.}

\label{main results pixel-wise}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.49\textwidth]{BCZContrastR1R3_TmS_sigp.pdf}
\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigp.pdf}
\caption{
  Estimated projected radially averaged velocity dispersion (\eqnref{eqn:sphericaljeans}) $\sigma_p$ for two Sdom/DMcuspy models ZContrastR1R3
  (left) and QuadR1a (right) assuming an anisotropy $\beta=0$ (blue, solid) and $\beta=1$
  (blue, dashed).  Also shown are the equivalent curves for the mock data after
  running it through the deprojection routines (grey). The solid black line is
  the actual cylindrically averaged velocity dispersion of the original mock particle data.
  The stellar half mass radius (yellow) Einstein
radius (black) are marked by vertical lines. For this configuration, these two
radii are well-separated.}
  \label{fig:sigp} \end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigpbar.pdf}
\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigpbar.pdf}
\caption{{\bf Left:} 
The mean projected velocity dispersion (\eqnref{eqn:virialaverage}) as a function of the upper
limit of the averaging integral (the aperture size), $a_p$
  for two Sdom/DMcuspy models ZContrastR1R3
  (left) and QuadR1a (right) assuming two extrema velocity anisotropies $\beta=0$ (blue, solid) and $\beta=1$
  (blue, dashed).  Also shown are the equivalent curves for the mock data after
  running it through the deprojection routines (grey). 
\sout{Over-plotted is the correct answer for the BC model (black)
  {\bf JR. Jonathan to add}.} 
  The stellar half mass radius (yellow) Einstein
radius (black) are marked by vertical lines. For this configuration, these two
radii are well-separated.}
\label{sigma-beta}
\end{figure*}

>>>>

\newcommand{\mockAA}{{\sc Ssteep-DMshallow}}
\newcommand{\mockAC}{{\sc Ssteep-DMsteep}}
\newcommand{\mockBB}{{\sc Ssteep-DMshallow}}
\newcommand{\mockBC}{{\sc Ssteep-DMsteep}}

@@

\begin{table}
\begin{tabular}{llllllll}
Galaxy & $\gamma_\star$ & $M_\star$ & $\gamma_\mathrm{DM}$ & $M_\mathrm{DM}$ & $\Rmap$ \\
\hline
\mockAA & 1 & 4 & 0.05 & $11^{2.95}$ & 50 kpc\\ % AA
\mockAC & 1 & 4 & 1 & $11^2$ & 50 kpc \\ % AC
\mockBB & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ & 50 kpc \\ % BB
\mockBC & 1.5 & $2^{1.5}$ & 1 & $11^2$ & 10 kpc %BC
\end{tabular}
\caption{Profile parameters for the four mock galaxies. The name indicates whether 
  the galaxy is centrally dark matter or stellar dominated with a shallow or cuspy 
  dark matter density profile.  Masses are in units of
  $1.8\e{10}\Msun$. The scale lengths for all lenses are
  $(a_\star,a_\mathrm{DM})=(2,20)$\,kpc. $\Rmap$ is the 2D projected radius
used to generate the lens configurations.}
\label{mock galaxy params}
\end{table}

@@

\begin{figure*}
  \includegraphics[width=0.35\textwidth]{BCQuadR1a_TmS-a.pdf}\hspace{-2em}
  \includegraphics[width=0.35\textwidth]{BCQuadR1a_TmS-b.pdf}\hspace{-2em}
  \includegraphics[width=0.35\textwidth]{BCQuadR1a_TmS-c.pdf}\\\vspace{-1em}
  \includegraphics[width=0.35\textwidth]{ACQuadR1a_TmS-a.pdf}\hspace{-2em}
  \includegraphics[width=0.35\textwidth]{ACQuadR1a_TmS-b.pdf}\hspace{-2em}
  \includegraphics[width=0.35\textwidth]{ACQuadR1a_TmS-c.pdf}
\caption{
  \sout{{\bf JR. Need to homogenise plot dimensions here. Larger fonts as in Figure 1 are also required.} }
A typical reconstructed lens. Here we present results for a single quad image lensed by the Sdom/DMcuspy mock galaxy.
\textbf{Left:}
The arrival time surface. 
\textbf{Middle:}
The surface density. The magenta curve represents the dark matter component,
the yellow curve the stellar component, and the blue curve is the sum of the two.
The black curve comes from the original mass model used to create the lens.
The green vertical lines mark the radial positions of the images. The higher
resolution feature of \Glass\ has been used on the central pixel allowing the
steep profile to be captured.
\textbf{Right:}
The cumulative mass. The error bars on all plots are $1\sigma$, but the grey area shows the full range for DM+Stars (blue).}
\label{reconstruction}
\end{figure*}

@@

\begin{figure}[h]
\plottwo{AAExtendedDoubleR1_TmS-shape-hist-11.pdf}{BCZContrastR1R3_TmS-shape-hist-212.pdf}
\caption{ The two plots in the left most column show sample distributions of
  $s=\lambda_1/\lambda_2$, the ratio of the largest to smallest principal axes.
  The upper (poor) plot is from the DMdom/DMshallow galaxy, while the lower (good) plot is
  from the Sdom/DMcuspy galaxy. The black vertical lines mark the $1\sigma$
  region and the vertical blue line is the value of $s$ for the corresponding
mock galaxy. }

\label{shape results}
\end{figure}

\begin{figure*}
  \includegraphics[width=0.33\textwidth]{AAferror_shape-1sig.pdf} \hspace{2cm}
\includegraphics[width=0.33\textwidth]{BBferror_shape-1sig.pdf}\\
\includegraphics[width=0.33\textwidth]{ACferror_shape-1sig.pdf}\hspace{2cm}
\includegraphics[width=0.33\textwidth]{BCferror_shape-1sig.pdf}
\caption{ The remain four plots are similar to those in \figref{main
  results pixel-wise} and show the fractional error of $s$ over all the models,
with respect to the mock galaxies.}

\label{shape results}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.33\textwidth]{BC_beta.pdf}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_Tms_sigp-1.pdf}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS_sigp-2.pdf}
\caption{
  Estimated projected radially averaged velocity dispersion (\eqnref{eqn:sphericaljeans}) $\sigma_p$ for two Sdom/DMcuspy models ZContrastR1R3
  (left) and QuadR1a (right) assuming an anisotropy $\beta=0$ (blue, solid) and $\beta=1$
  (blue, dashed).  Also shown are the equivalent curves for the mock data after
  running it through the deprojection routines (grey). The solid black line is
  the actual cylindrically averaged velocity dispersion of the original mock particle data.
  The stellar half mass radius (yellow) Einstein
radius (black) are marked by vertical lines. For this configuration, these two
radii are well-separated.}
  \label{fig:sigp} \end{figure*}

@@

%\begin{figure*}
%\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigpbar.pdf}
%\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigpbar.pdf}
%\caption{{\bf Left:} 
%The mean projected velocity dispersion (\eqnref{eqn:virialaverage}) as a function of the upper
%limit of the averaging integral (the aperture size), $a_p$
%  for two Sdom/DMcuspy models ZContrastR1R3
%  (left) and QuadR1a (right) assuming two extrema velocity anisotropies $\beta=0$ (blue, solid) and $\beta=1$
%  (blue, dashed).  Also shown are the equivalent curves for the mock data after
%  running it through the deprojection routines (grey). 
%\sout{Over-plotted is the correct answer for the BC model (black)
%  {\bf JR. Jonathan to add}.} 
%  The stellar half mass radius (yellow) Einstein
%radius (black) are marked by vertical lines. For this configuration, these two
%radii are well-separated.}
%\label{sigma-beta}
%\end{figure*}
